Carbonate chemistry at Ny-Ålesund

### 2021-02-19 awipev-CO2.Rmd
idem
calculations of min.max/mean of SD for spectro pH

# Make mean for replicates. create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(date, ph_s_sf_temp_insi)%>% 
  dplyr::group_by(date) %>% 
  dplyr::summarize(ph_s_sf_temp_insi = mean(ph_s_sf_temp_insi, na.rm = TRUE))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(date, ph_s_dur_temp_fb)%>% 
  dplyr::group_by(date) %>% 
  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = TRUE))

@@

rm(d_min)
```

>>>>

# Make mean for replicates + SD
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(date, ph_s_sf_temp_insi)%>% 
  dplyr::group_by(date) %>% 
  dplyr::summarise(ph_s_sf_temp_insi_mean = mean(ph_s_sf_temp_insi, na.rm = TRUE),
                   ph_s_sf_temp_insi_sd= sd(ph_s_sf_temp_insi, na.rm = TRUE)
                   )

pH_durafet_mean <- pH_durafet%>%
  dplyr::select(date, ph_s_dur_temp_fb)%>% 
  dplyr::group_by(date) %>% 
  dplyr::summarize(ph_s_dur_temp_fb_mean = mean(ph_s_dur_temp_fb, na.rm = TRUE),
                   ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE))

#bind all spectro measurements, vhange name of dataframe only to do the rbind.
seafetph <- pH_seafet_mean
colnames(seafetph) <- c("date", "mean", "sd")
durafetph <- pH_durafet_mean
colnames(durafetph) <- c("date", "mean", "sd")
pH_seafet_durafet <- rbind(seafetph,durafetph)

#calculations for all pH spectro measurement for sd
sd_min <- min(pH_seafet_durafet$sd)
sd_max <- max(pH_seafet_durafet$sd)
sd_mean <- mean(pH_seafet_durafet$sd)

@@

#rm(d_min)
```
